Describing vocalizations in young children: A big data approach through citizen science annotation

### 2021-05-26 202010_jslhr/paper.Rmd
correcting typos

```{r fig-process, comment=F, message=F, hide = T, warning = F, echo = F, fig.cap = "Correspondence between LENA-identified segments (which can contain one or more vocalizations) and chunks. Segments and chunks are collectively referred to as clips because they are parts of the longer audio recording. Notice that clips are first annotated by multiple people, and these judgments are then combined into a single label based on simple majority. To compare laboratory and Zooniverse annotations at the level of segments, chunk-level labels are combined using the hierarchy Canonical > Non-canonical > Crying > Laughing > Junk."}
knitr::include_graphics("fig_levels.key.pdf")

@@

prettynames=c("Linguistic Proportion (Zoon.)","Canonical Proportion (Zoon.)",
             "Linguistic Proportion (Lab)","Canonical Proportion (Lab)" )
names(prettynames)<-c("z_lp","z_cp","l_lp","l_cp")
mycols=c("black","red")
names(mycols)<-c("Low-RiskControl","AngelmanSyndrome")
mypch=c(4,20)
names(mypch)<-c("Low-RiskControl","AngelmanSyndrome")

@@

#create matrix to hold r results
myr=matrix(NA,nrow=4,ncol=2)
rownames(myr)<-c("z_lp","z_cp","l_lp","l_cp")
colnames(myr)<-c("AS","LR")
mylb=myhb=myn=myp =myr #this is an ugly way of creating 5 matrices

@@

  plot(proportions[,thisvar]~proportions$Age, pch=mypch[proportions$Diagnosis],xlab="Age (months)",ylab=prettynames[thisvar],
       col=mycols[proportions$Diagnosis],
         ylim=myrange)
  abline(lm(proportions[,thisvar]~proportions$Age,subset=c(proportions$Diagnosis=="AngelmanSyndrome")),col="black")

@@

    #add r to figure
  text(mean(proportions$Age[proportions$Diagnosis=="AngelmanSyndrome"]),mean(proportions[proportions$Diagnosis=="AngelmanSyndrome",thisvar]),paste0("r=",myr[thisvar,"AS"]),col="black")

@@

    text(mean(proportions$Age[proportions$Diagnosis!="AngelmanSyndrome"]),mean(proportions[proportions$Diagnosis!="AngelmanSyndrome",thisvar]),paste0("r=",myr[thisvar,"LR"]),col="red")
}
#dev.off()
```

@@

  abline(lm(proportions[,"z_cp"]~proportions[,"l_cp"],subset=c(proportions$Diagnosis=="AngelmanSyndrome")),col="black")

@@

#add zoo & lab data
recalls=round(stall_r$rec[stall_r$Lab==stall_r$Zooniverse],1)
names(recalls)<-c("Canonical","Crying","Junk","Laughing","Non-can.")
recalls=recalls[as.character(tab1[2:6,"X"])]
freqs=table(data_all$Zoon)
names(freqs)<-c("Canonical","Crying","Junk","Laughing","Non-can.")
freqs=freqs[as.character(tab1[2:6,"X"])]
w=freqs/sum(freqs)
UAR=round(mean(recalls),1)
WAR=round(weighted.mean(recalls,w),1)
tab1$z=c("Zoon.",recalls, UAR,WAR)
tab1$f=c("Zoon.",freqs, "","")
tab1=tab1[,c("X","Recall","x","z","Label.frequency","f")]
write.csv(tab1,"tab1-final.csv",row.names=F)
#olnames(tab1)<-c("","Recall","Recall","Recall","Label Frequency","Label Frequency")

>>>>

```{r fig-process, comment=F, message=F, hide = T, warning = F, echo = F, fig.cap = "Correspondence between LENA-identified segments (which can contain one or more vocalizations) and chunks. Segments and chunks are collectively referred to as clips because they are parts of the longer audio recording. Notice that clips are first annotated by multiple people, and these judgments are then combined into a single label based on simple majority. To compare laboratory and Zooniverse annotations at the level of segments, chunk-level labels are combined using the hierarchy Canonical > Non-canonical > Crying > Laughing > Junk."}
knitr::include_graphics("fig_levels.pdf")

@@

prettynames=c("Linguistic Proportion (Zoon.)","Canonical Proportion (Zoon.)",
             "Linguistic Proportion (Lab)","Canonical Proportion (Lab)" )
names(prettynames)<-c("z_lp","z_cp","l_lp","l_cp")
mycols=c("red","black")
names(mycols)<-c("Low-RiskControl","AngelmanSyndrome")
mypch=c(4,20)
names(mypch)<-c("Low-RiskControl","AngelmanSyndrome")

@@

#create matrix to hold r results
myr=matrix(NA,nrow=4,ncol=2)
rownames(myr)<-c("z_lp","z_cp","l_lp","l_cp")
colnames(myr)<-c("AS","LR")
mylb=myhb=myn=myp =myr #this is an ugly way of creating 6 matrices

#to improve legibility of figures, providing the coordinates to offset the text
mytext<-rbind(
  cbind(-.1,-.1,0,-.2), #"z_lp"
  cbind(+.1,+.1,-.1,+.3), #"z_cp"
  cbind(-.1,-.1,0,-.2), #"l_lp"
  cbind(+.1,+.1,-.1,+.25) #"l_cp"
)
rownames(mytext)<-c("z_lp","z_cp","l_lp","l_cp")
colnames(mytext)<-c("AS.x","AS.y","LR.x","LR.y")

@@

  plot(proportions[,thisvar]~proportions$Age, pch=mypch[proportions$Diagnosis],xlab="Age (months)",ylab=prettynames[thisvar],
       col=mycols[proportions$Diagnosis],
         ylim=myrange)
  abline(lm(proportions[,thisvar]~proportions$Age,subset=c(proportions$Diagnosis=="AngelmanSyndrome")),col="black",lty=2)

@@

    #add r to figure
  text(
    mean(proportions$Age[proportions$Diagnosis=="AngelmanSyndrome"])+mytext[thisvar,"AS.x"],mean(proportions[proportions$Diagnosis=="AngelmanSyndrome",thisvar])+mytext[thisvar,"AS.y"],
    paste0("r=",myr[thisvar,"AS"]),col="black")

@@

    text(mean(proportions$Age[proportions$Diagnosis!="AngelmanSyndrome"])+mytext[thisvar,"LR.x"],
         mean(proportions[proportions$Diagnosis!="AngelmanSyndrome",thisvar])+mytext[thisvar,"LR.y"],
         paste0("r=",myr[thisvar,"LR"]),col="red")
}
#dev.off()
```

@@

  abline(lm(proportions[,"z_cp"]~proportions[,"l_cp"],subset=c(proportions$Diagnosis=="AngelmanSyndrome")),col="black",lty=2)

@@

#add zoo & lab data
recalls=round(stall_r$rec[stall_r$Lab==stall_r$Zooniverse],1)
names(recalls)<-stall_r$Lab[stall_r$Lab==stall_r$Zooniverse]
names(recalls)[names(recalls)=="Non-Canonical"]<-"Non-can."
  #c("Canonical","Crying","Junk","Laughing","Non-can.")
recalls=recalls[as.character(tab1[2:6,"X"])]
freqs=table(data_all$Zoon)
names(freqs)[names(freqs)=="Non-Canonical"]<-"Non-can."
freqs=freqs[as.character(tab1[2:6,"X"])]
w=freqs/sum(freqs)
UAR=round(mean(recalls),1)
WAR=round(weighted.mean(recalls,w),1)
tab1$z=c("Zoon.",recalls, UAR,WAR)
tab1$f=c("Zoon.",freqs, "","")
tab1=tab1[,c("X","Recall","x","z","Label.frequency","f")]
write.csv(tab1,"tab1-final.csv",row.names=F)
#olnames(tab1)<-c("","Recall","Recall","Recall","Label Frequency","Label Frequency")
